---
title: "Week_1"
author: "Jingyao ZHOU"
date: "12/1/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Input and output
```{r}
x<-1
print(x)
msg<-"hello" #hash symbol for comment
msg # auto-printing occurs
y<-1:20 # : sequencing 
y
```



## Attribute

R has five "atomic" classes of objects

- character
- real number
- integer
- complex
- logical

**vector** is the most basic object
```{r}
vector() # to create empty vector
```
Number is generally treated as a numeric object, if want an integer, add L suffix
```{r}
x1=1
x2=1L
str(x1)
str(x2)
```
Inf represents infinity
NaN: not a number

Objects have attributes

- names
- dimensions
- class
- length
- user-defined attributes

can be accessed using 
> attributes()

**Mixing objects**
```{r}
y1<-c(1.7,"a")
y2<-c(TRUE,2)
y3<-c("a",TRUE)
str(y1)
str(y2)
str(y3)

```
**Conversion** 
as.
```{r}
x<-0:6
class(x)
as.numeric(x)
as.logical(x)
as.character(x)
```
**Lists**
```{r}
x<-list(1,"a",TRUE,1+4i)
x
```
**Matrices**
```{r}
m<-matrix(nrow =2, ncol=3)
m
dim(m)
```
Matrices are constructed column-wise, 先按列排，再按横排
```{r}
m<-matrix(1:6,nrow=2,ncol=3)
m
```
Adding dimension attribute
```{r}
m<-(1:10)
dim(m)<-c(2,5)
m
```
**Factors**
Factors are used to represent categorical data
```{r}
x<-factor(c("yes","yes","no"))
x
table(x)
x
```
The level of the factors are set based on alphabet, "no"优先于"yes"
用 levels 调整
```{r}
x<-factor(c("yes","yes","no"),levels = c("yes","no"))
x
```
**Missing values**
denoted as NA (everything else)or NaN (undefined mathematical operations)
```{r}
x<-c(1,2,NaN,NA,4)
is.na(x)
```
**Data frame**
```{r}
x<-data.frame(foo=1:4,bar=c(T,T,F,F))
x
```
**Names**
Give objects names
```{r}
x<-1:3
names(x)
names(x)<-c("a","b","c")
names(x)
```
Names of lists
```{r}
x<-list(a=1,b=2,c=3,4)
x
```
Names of matrices
```{r}
m<-matrix(1:4,nrow=2,ncol=2)
dimnames(m)<-list(c("a","b"),c("c","d"))
m
```

